\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-27 OaklandSubmission/intro.tex
intro

\subsubsection*{Scalability (secure code partitioning)} \mpc tools
often do not scale to large programs. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data. \aseem{Can we
cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we break the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue -- it automatically inserts the required instrumentation
to ensure security in the presence of these intermediate outputs. As
we show in our
evaluation, partitioning allows us to program large applications
in \tool.

@@

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem proves a
forward simluation between the
``ideal'' semantics (the trusted-third party semantics) of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The simulation
theorem not only guarantees that a
well-typed source program terminates successfully in the ideal
semantics (e.g. there are no array index out-of-bounds errors), but
also that the observable outputs in the two semantics are the same. For
the security theorem, we formally reduce the security
of our compiler to the security of the back-end cryptographic
protocol. We also prove a formal security theorem for our partitioning
scheme.

@@

%% {\aseem{Not sure about this baseline paragraph. Did not touch it.}} 
%% \subsubsection*{Performance Baseline} Most works cite garbled
%% circuit based two-party computation as the most practical approach so
%% far and use it as the baseline for comparison of performance. But, it
%% has been shown multiple times that the garbled circuits based approach
%% does not scale for realistic examples. Even for small benchmarks
%% (e.g., Na\"{i}ve Bayes) the size of garbled circuit can be
%% huge. Hence, comparisons are often done on artificial data sizes and
%% garbled circuits are shown to be 500x slower than hand-crafted
%% protocols \cite{shafindss}. This is cited as the motivation for need
%% for specialized protocols for different ML algorithms in secure
%% prediction such as linear regression \cite{shafindss}, decision
%% trees \cite{wu}, deep neural networks \cite{minionn} and matrix
%% factorization \cite{valeriaMatrix}. Our work is based on generic \mpc
%% and we show competitive performance with the specialized protocols
%% contrary to the popular belief. Hence, we believe \tool based
%% implementations can serve as the performance baseline for future works
%% on specialized protocols.

@@

\aseem{Checkpointing here. Three more paragraphs to come, one for
summary of implementation and evaluation, one for related work, and
one for baseline argument.}

\noindent\textbf{Other Related Work.} 
Before ABY \cite{aby}, to improve efficiency, several works proposed
to mix secure computation protocols based on homomorphic
encryption and Yao's garbled circuits protocol, e.g., \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}
  and developed tools that allowed writing a mixed \mpc protocol, e.g., \cite{bogdanov,lone,tasty}. The breaking up of the function into homomorphic encryption and garbled circuits can
even be done automatically as was shown in \cite{autoS}. 
However, as was noted by ABY, due to high conversion cost between homomorphic encryption and Yao's garbled circuit, these mixed protocols do not gain much performance over a single protocol. Also, none of these works give a high-level developer-friendly language support.
No prior work has given a formal type system and operational semantics for mixed arithmetic and boolean back-ends.
We provide a detailed survey of related work in \sectionref{related}.

>>>>

\subsubsection*{Scalability (secure code partitioning)} \mpc tools
often do not scale to large programs. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we break the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue -- it automatically inserts the required instrumentation
to ensure security of these intermediate outputs. As
we show in our
evaluation, partitioning allows us to program large applications
in \tool.

@@

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem proves a
forward simluation between the
``ideal'' semantics (the trusted-third party semantics) of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The simulation
guarantees that for a well-typed source program, the two semantics
successfully terminate
(e.g. there are no array index out-of-bounds errors), and that the
observable outputs in the two semantics are
identical. For
the security theorem, we formally reduce the security
of our compiler to the security of the back-end cryptographic
protocol. We also prove a formal security theorem for our partitioning
scheme.

We have implemented the \tool toolchain using ABY~\cite{aby} as the
cryptographic back-end. We evaluate \tool by implementing a wide range
of secure prediction benchmarks including linear and na\"{i}ve bayes
classifiers, decision trees, deep neural networks, state-of-the-art
classifiers such as Tensorflow~\cite{tensorflow}
and \bonsai~\cite{bonsai}, and also the matrix factorization example
from Nikolaenko et al.~\cite{valeriaMatrix}. Our results demonstrate
three key points. First, \tool makes it convenient for general
programmers to write \mpc protocols. E.g. we provide the first \mpc
implementation of \bonsai~\cite{bonsai}, and it was programmed at a
high-level in \tool by a
cryptography novice. Second, the performance of the protocols
generated by \tool are comparable to or better than (up to 19x in some
cases) their state-of-the-art specialized implementations. Finally, we
show that with partitioning, we are able to implement applications
that require more than 100 million gates.

The rest of the paper is structured as follows. We formalize \tool and
prove its correctnss and security theorems in
Section~\ref{sec:ld}. Section~\ref{sec:pipe} details our partitioning
scheme and formally proves its security. Section~\ref{sec:impl}
and~\ref{sec:eval} present details of \tool implementation and
evaluation. Finally, Section~\ref{sec:related} talks about the related
work. We start with an overview of \tool.

%% Most works cite garbled
%% circuit based two-party computation as the most practical approach so
%% far and use it as the baseline for comparison of performance. But, it
%% has been shown multiple times that the garbled circuits based approach
%% does not scale for realistic examples. Even for small benchmarks
%% (e.g., Na\"{i}ve Bayes) the size of garbled circuit can be
%% huge. Hence, comparisons are often done on artificial data sizes and
%% garbled circuits are shown to be 500x slower than hand-crafted
%% protocols \cite{shafindss}. This is cited as the motivation for need
%% for specialized protocols for different ML algorithms in secure
%% prediction such as linear regression \cite{shafindss}, decision
%% trees \cite{wu}, deep neural networks \cite{minionn} and matrix
%% factorization \cite{valeriaMatrix}. Our work is based on generic \mpc
%% and we show competitive performance with the specialized protocols
%% contrary to the popular belief. Hence, we believe \tool based
%% implementations can serve as the performance baseline for future works
%% on specialized protocols.

@@

%% {\aseem{Not sure about this baseline paragraph. Did not touch it.}}

@@

%% \aseem{Checkpointing here. Three more paragraphs to come, one for
%% summary of implementation and evaluation, one for related work, and
%% one for baseline argument.}

%% \noindent\textbf{Other Related Work.} 
%% Before ABY \cite{aby}, to improve efficiency, several works proposed
%% to mix secure computation protocols based on homomorphic
%% encryption and Yao's garbled circuits protocol, e.g., \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}
%%   and developed tools that allowed writing a mixed \mpc protocol, e.g., \cite{bogdanov,lone,tasty}. The breaking up of the function into homomorphic encryption and garbled circuits can
%% even be done automatically as was shown in \cite{autoS}. 
%% However, as was noted by ABY, due to high conversion cost between homomorphic encryption and Yao's garbled circuit, these mixed protocols do not gain much performance over a single protocol. Also, none of these works give a high-level developer-friendly language support.
%% No prior work has given a formal type system and operational semantics for mixed arithmetic and boolean back-ends.
%% We provide a detailed survey of related work in \sectionref{related}.
